IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2020-10-09 main.tex
:art: Rephrase literature review

\begin{document}
	\title{IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design}
	\author{
		\IEEEauthorblockN{
			Yang~Zhao,~\IEEEmembership{Member,~IEEE}
			and~Bruno~Clerckx,~\IEEEmembership{Senior~Member,~IEEE}
		}
		\thanks{
			The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: yang.zhao18@imperial.ac.uk; b.clerckx@imperial.ac.uk).
		}
	}
	\maketitle

	\begin{abstract}
		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly restricted by the strength of the received Radio-Frequency (RF) signal. To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates the propagation loss and boosts the energy efficiency with a passive beamforming gain. This paper investigates an IRS-aided Orthogonal Frequency Division Multiplexing (OFDM) SWIPT system based on a practical nonlinear energy harvester model, where a multi-antenna Access Point (AP) transmits information and energy simultaneously to a single-antenna user under the assist of IRS. We aim to maximize the Rate-Energy (R-E) region through a joint optimization of the transmit waveform, active beamforming at the AP, and passive beamforming at the IRS. The performance of the proposed design is compared with those of no IRS, non-adaptive IRS and ideal Frequency-Selective (FS) IRS, and we confirm that due to rectifier nonlinearity, a dedicated power signal can be beneficial to energy harvesting (EH). It has the consequence that the Time-Switching (TS) receiver is preferred over Power-Splitting (PS) receiver for multi-carrier transmission at a low Signal-to-Noise Ratio (SNR). Simulation results demonstrate that the adaptive IRS design leads to significant R-E enhancement over benchmark schemes for broadband transmission, and the optimal IRS can be approximated in closed form with negligible performance loss for narrowband transmission.
	\end{abstract}

@@

	\begin{section}{Introduction}
		\begin{subsection}{Simultaneous Wireless Information and Power Transfer}
			\IEEEPARstart{W}{ith} the great advance in communication performance, the bottleneck of wireless networks is coming to energy supply. Most existing mobile devices are powered by batteries that require frequent charging or replacement, which causes high maintenance cost and restricts the scale of networks. Although solar energy and inductive coupling have become popular alternatives, the former depends on the environment while the latter has a very short operation range. Simultaneous Wireless Information and Power Transfer (SWIPT) is a promising solution to connect and power mobile devices via electromagnetic (EM) waves in the Radio-Frequency (RF) band. It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner \cite{Clerckx2018a}, bringing more opportunities to the Internet of Things (IoT) and Machine to Machine (M2M) networks. Meantime, the reduction in electronics power consumption and the explosion of mobile devices also call for a paradigm shift from dedicated information and power sources to SWIPT.

			The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels. Two co-localized information and power receivers were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between Energy Harvesting (EH) and Information Decoding (ID) modes, and Power Splitting (PS) that splits the received signal into individual components. Dedicated information and energy beamforming were then introduced in \cite{Zhang2013} to characterize the R-E region for a Multiple-Input Multiple-Output (MIMO) broadcast system. From the perspective of Wireless Power Transfer (WPT), \cite{Trotter2009} pointed out that the Radio Frequency-to-Direct Current (RF-to-DC) conversion efficiency depends on the harvester input power level. The authors recommended waveforms with large Peak-to-Average Power Ratio (PAPR), such as multisine, to improve the power efficiency and system coverage. Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics. Simulation and experiments demonstrated the benefit of modeling harvester nonlinearity on WPT system design \cite{Kim2019,Kim2019a}. On the other hand, \cite{Clerckx2018b} proposed a waveform design for SWIPT where a multisine power component was superposed to a modulated information component to enlarge the R-E region.
		\end{subsection}

		\begin{subsection}{Intelligent Reflecting Surface}
			Intelligent Reflecting Surface (IRS) adjusts the wireless channel to increase spectrum and energy efficiency. In practice, an IRS consists of multiple individual reflecting elements that modify the amplitude and phase of the incident signal through passive beamforming. Different from relay and backscatter, IRS assists the primary transmission using fully passive components, thus consumes less power with no additional thermal noise but is limited to frequency-flat (FF) reflection. Although Frequency-Selective Surface (FSS) has received much attention for wideband communications, it is different from IRS as active FSS requires RF-chains \cite{Kim2006} while passive FSS has fixed physical characteristics and is non-adaptive \cite{Anwar2018}.

			Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at specific frequency to mitigate signal attenuation. Motivated by this, \cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power. The active and passive beamforming problem was extended to the discrete phase shift case \cite{Wu2019a} and the multiuser case \cite{Wu2019}. Starting from the impedance equation, \cite{Abeywickrama2019} investigated the influence of phase shift on the reflection amplitude and proposed a parametric IRS model via curve fitting.	In \cite{Nadeem2019}, channel estimation for Time-Division Duplex (TDD) systems was carried through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially estimates the cascaded channel through each reflector with the others switched off. To reduce estimation overhead and design complexity, \cite{Yang2019} exploited the spatial correlation and proposed a group-based IRS model where adjacent elements share a common reflection coefficient. Recent research also explored the possibility of integrating IRS into Orthogonal Frequency-Division Multiplexing (OFDM) systems. For example, \cite{Yang2020} further enhances time diversity by dynamic passive beamforming that varies IRS over consequent time slots, which enables flexible resource allocation over time-frequency Resource Blocks (RBs). In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency.
		\end{subsection}

		\begin{subsection}{IRS-aided SWIPT}
			The effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT. It was argued in \cite{Wu2019b} that dedicated energy beam is not required to maximize the Weighted Sum-Power (WSP) for a multiuser IRS-assisted SWIPT system, which is power-inefficient and may cause interference. On the other hand, \cite{Tang2019} suggested that if the interference from energy signals can be cancelled, multiple energy beams are generally required for the max-min harvested power problem. \cite{Wu2019c} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update transmit precoders and IRS phase shifts while the outer layer updates the penalty coefficients. It demonstrated that Line-of-Sight (LoS) links can boost the harvested power because the rank-deficient channels are highly correlated. In such cases, a single energy stream can satisfy the energy constraints of all energy receivers.
			% However, most existing IRS-assisted SWIPT papers focused on narrow-band transmission for separated information and energy receivers based on an oversimplified linear harvester model.
		\end{subsection}

@@

			\textit{Organization:} The rest of this paper is organized as follows. Section~\ref{se:system_model} introduces the signal, channel, information decoder, energy harvester, and R-E tradeoff models of the IRS-aided SWIPT system. Section~\ref{se:problem_formulation} tackles the waveform, active and passive beamforming optimization. Section~\ref{se:performance_evaluation} presents simulation results to evaluate the proposed design. Section~[TODO] concludes the paper.

			\textit{Notations:} Scalars are denoted by italic letters, vectors are denoted by bold lower-case letters, and matrices are denoted by bold upper-case letters. $j$ refers to the imaginary unit. $\mathbb{C}^{x \times y}$ denotes the subspace spanned by complex $x \times y$ matrices. $\Re\{\cdot\}$ and $\Im\{\cdot\}$ stand for the real and imaginary part of a complex number or variable, respectively. $(\cdot)^*$, $(\cdot)^T$ and $(\cdot)^H$ represent the conjugate, transpose, and conjugate transpose operators, respectively. $\mathcal{A}\{\cdot\}$ extracts the DC component of a signal, and $\mathcal{E}_X\{\cdot\}$ takes the expectation over the distribution of the random variable $X$ ($X$ may be omitted for simplicity). For a scalar $x$, $\lvert{x}\rvert$ denotes its absolute value. For a vector $\boldsymbol{x}$, $\lVert{\boldsymbol{x}}\rVert$ refers to its Euclidean norm, $\arg(\boldsymbol{x})$ refers to its argument vector, and $\mathrm{diag}(\boldsymbol{x})$ refers to a square diagonal matrix with the elements of $\boldsymbol{x}$ on the main diagonal. For a general matrix $\boldsymbol{M}$, $\mathrm{rank}(\boldsymbol{M})$ denotes it rank. For a square matrix $S$, $\mathrm{Tr}(\boldsymbol{S})$ denotes its trace, and $\boldsymbol{S} \succeq 0$ means that $\boldsymbol{S}$ is positive semi-definite. The distribution of a Circularly Symmetric Complex Gaussian (CSCG) random vector with mean vector $\boldsymbol{\mu}$ and covariance matrix $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{\mu},\boldsymbol{\Sigma})$ and $\sim$ stands for "distributed as". We also denote $(\cdot)^{\star}$ and $(\cdot)^{(i)}$ as stationary solution and solution at iteration $i$, respectively.
		\end{subsection}
	\end{section}

@@

		As shown in Fig.~\ref{fi:system}, we consider an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-reflector IRS, to a single-antenna user over $N$ orthogonal evenly-spaced subbands with center frequency $f_n$ ($n=1,\dots,N$). Perfect Channel State Information (CSI) of all channels are assumed at the AP. A quasi-static block fading channel model is considered for all links, and we focus on one particular block where the channels are approximately unchanged. Two practical co-located receiver architectures are compared in terms of R-E region. Specifically, TS divides each time slot into orthogonal data and energy slots and performs a time sharing between WPT and Wireless Information Transfer (WIT). In comparison, PS splits the received signal into individual ID and EH streams such that the splitting ratio $\rho$ is coupled with waveform and IRS design. Perfect synchronization is assumed among the three parties in both scenarios, and signals reflected by IRS for two and more times are omitted. We also assume the noise power is too small to be harvested.

@@

		\begin{subsection}{Composite Channel}
			At subband $n$, denote the AP-user direct channel as $\boldsymbol{h}_{D,n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$, and IRS-user reflective channel as $\boldsymbol{h}_{R,n}^H \in \mathbb{C}^{1 \times L}$. At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection amplitude $\gamma_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$~\footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\gamma_l=1\,,\forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}. Define the IRS matrix as $\boldsymbol{\Theta} = \mathrm{diag}(\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$ that collects the reflection coefficients onto its main diagonal entries. The extra link introduced by IRS can be modeled as a concatenation of the AP-IRS incident channel, IRS reflection matrix, and IRS-user reflective channel. Hence, the total composite channel is obtained by superposing the IRS-aided extra channel to the AP-user direct channel as
			\begin{equation}\label{eq:h_n}
				\boldsymbol{h}_{n}^H = \boldsymbol{h}_{D,n}^H + \boldsymbol{h}_{R,n}^H \boldsymbol{\Theta} \boldsymbol{H}_{I,n} = \boldsymbol{h}_{D,n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n}
			\end{equation}
			where $\boldsymbol{\phi}=[\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{n}=\mathrm{diag}(\boldsymbol{h}_{R,n}^H)\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$. Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.
		\end{subsection}

@@

	\begin{section}{Problem Formulation}\label{se:problem_formulation}
		We characterize the R-E region through a current maximization problem subject to transmit power, IRS magnitude, and different rate constraints
		\begin{maxi!}
			{\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho}{z(\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho)}{\label{op:original}}{\label{ob:original}}
			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_I}\rVert^2+\lVert{\boldsymbol{w}_P}\rVert^2\right)\le{P}}\label{co:original_power}
			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_I,\rho) \ge \bar{R}}\label{co:original_rate}
			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}\label{co:original_modulus}
			\addConstraint{0 \le \rho \le 1\,.}
		\end{maxi!}
		Problem~\ref{op:original} is intricate due to non-convex objective function \ref{ob:original} and rate constraint \ref{co:original_rate} with coupled variables. To reduce the design complexity, we propose a suboptimal AO algorithm that iteratively updates the IRS phase shift and transmit waveform plus the receive splitting ratio until convergence.

>>>>

\begin{document}
	\title{IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design}
	\author{
		\IEEEauthorblockN{
			Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
			~Bruno~Clerckx,~\IEEEmembership{Senior~Member,~IEEE}
			and~Zhenyuan~Feng,~\IEEEmembership{Member,~IEEE}
		}
		\thanks{
			The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: yang.zhao18@imperial.ac.uk; b.clerckx@imperial.ac.uk).
		}
	}
	\maketitle

	\begin{abstract}
		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly restricted by the strength of the received Radio-Frequency (RF) signal. To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates the propagation loss and boosts the energy efficiency with a passive beamforming gain. This paper investigates an IRS-aided Orthogonal Frequency Division Multiplexing (OFDM) SWIPT system based on a practical nonlinear energy harvester model, where a multi-antenna Access Point (AP) transmits information and energy simultaneously to a single-antenna user under the assist of IRS. We aim to maximize the Rate-Energy (R-E) region through a joint optimization of the transmit waveform and active beamforming at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user. The performance of the proposed design is compared with those of no IRS, non-adaptive (information-optimized, power-optimized) IRS and ideal Frequency-Selective (FS) IRS, and we confirm that due to rectifier nonlinearity, a dedicated power signal can be beneficial to energy harvesting (EH). It has the consequence that the Time-Switching (TS) receiver is preferred over Power-Splitting (PS) receiver for multi-carrier transmission at a low Signal-to-Noise Ratio (SNR). Simulation results demonstrate that the proposed design based on a joint waveform, active and passive beamforming optimization brings significant R-E enhancement over benchmark schemes for broadband transmission, and the optimal IRS can be approximated in closed form with negligible performance loss for single transmit antenna narrowband SWIPT.
	\end{abstract}

@@

	\begin{section}{Introduction}
		\begin{subsection}{Simultaneous Wireless Information and Power Transfer}
			\IEEEPARstart{W}{ith} the great advance in communication performance, a bottleneck of wireless networks comes to energy supply. Most existing mobile devices are powered by batteries that require frequent charging or replacement, which causes high maintenance cost and restricts the scale of networks. Although solar energy and inductive coupling have become popular alternatives, the former depends on the environment while the latter has a very short operation range. Simultaneous Wireless Information and Power Transfer (SWIPT) is a promising solution to connect and power mobile devices via electromagnetic (EM) waves in the Radio-Frequency (RF) band. It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner, bringing more opportunities to the Internet of Things (IoT) and Machine to Machine (M2M) networks. The upsurge in the number of connected devices, together with the decreasing trend in the power consumption of electronics, call for a re-thinking of future wireless networks based on Wireless Power Transfer (WPT) and SWIPT \cite{Clerckx2019}.

			The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels. Two co-localized information and power receivers were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between Energy Harvesting (EH) and Information Decoding (ID) modes, and Power Splitting (PS) that splits the received signal into individual components. Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels.
			% Though SWIPT has been subsequently investigated in many scenarios \cite{Clerckx2019}, it was noticed more recently that the modeling of the energy harvester, and in particular its nonlinearity, has a crucial and significant impact on the signal preference, resource allocation and system design of WPT and any wireless-powered systems \cite{Trotter2009,Clerckx2016a,Clerckx2019}.
			% , and recommended waveforms with large Peak-to-Average Power Ratio (PAPR) to improve the power efficiency and system coverage
			On the other hand, \cite{Trotter2009} pointed out that the Radio Frequency-to-Direct Current (RF-to-DC) conversion efficiency depends on the rectifier input power level. It implies that the modeling of the energy harvester, in particular its nonlinearity, has a crucial and significant impact on the waveform preference, resource allocation and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}. Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then implemented joint waveform and beamforming design for WPT. Simulation and experiments demonstrated the inaccuracy of the rectenna linear model and emphasized the benefit of modeling the rectifier nonlinearity in real system design \cite{Kim2019,Kim2019a}. Importantly, the joint waveform and beamforming strategy for WPT was also shown experimentally in \cite{Kim2020} to be a key technique to expand operation range. %Beyond WPT, the work in [10]
			The work was extended to SWIPT in \cite{Clerckx2018b}. Uniquely, it showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely
			\begin{itemize}
				\item modulated and unmodulated waveforms are not equally suitable for wireless power delivery;
				\item a multicarrier unmodulated waveform superposed to a multicarrier modulated waveform is useful to enlarge the R-E region of SWIPT;
				\item combination of power splitting and time sharing is in general the best strategy;
				\item the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG);
				\item the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design.
			\end{itemize}
			Those observations, validated experimentally in \cite{Kim2019},  led to the question "what is the optimal input distribution for SWIPT under nonlinearity?". This question was answered in \cite{Varasteh2017} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019b} for multi-carrier SWIPT. The answer sheds new light to fundamental limits of SWIPT and practical signaling (e.g. modulation and waveform) strategies. It is now well understood from \cite{Clerckx2018b,Varasteh2017,Varasteh2019b} that, due to the nonlinearity, a combination of CSCG and On-Off Keying in single-carrier setting and non-zero mean and asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG. Recently, \cite{Varasteh2019a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information theoretic results of \cite{Varasteh2017} and new modulation schemes were subsequently designed.
		\end{subsection}

		\begin{subsection}{Intelligent Reflecting Surface}
			Intelligent Reflecting Surface (IRS) has recently emerged as a promising technique that adapts the wireless channel to increase spectrum and energy efficiency. In practice, an IRS consists of multiple individual reflecting elements that adjust the amplitude and phase of the incident signal through passive beamforming. Different from relay and backscatter, IRS assists the primary transmission using fully passive components, thus consumes less power with no additional thermal noise but is limited to frequency-flat (FF) reflection. Although Frequency-Selective Surface (FSS) has received much attention for wideband communications, it is different from IRS as active FSS requires RF-chains \cite{Kim2006} while passive FSS has fixed physical characteristics and is non-adaptive \cite{Anwar2018}.

			Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at specific frequency to mitigate signal attenuation. Motivated by this, \cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power. The active and passive beamforming problem was extended to the discrete phase shift case \cite{Wu2019a} and the multiuser case \cite{Wu2019}. Starting from the impedance equation, \cite{Abeywickrama2019} investigated the influence of phase shift on the reflection amplitude and proposed a parametric IRS model via curve fitting. In \cite{Nadeem2019}, channel estimation for Time-Division Duplex (TDD) systems was carried through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially estimates the cascaded channel through each reflector with the others switched off. To reduce estimation overhead and design complexity, \cite{Yang2019} exploited the spatial correlation and proposed a group-based IRS model where adjacent elements share a common reflection coefficient. Recent research also explored the possibility of integrating IRS into Orthogonal Frequency-Division Multiplexing (OFDM) systems. For example, \cite{Yang2020} further enhances time diversity by dynamic passive beamforming that varies IRS over consequent time slots, which enables flexible resource allocation over time-frequency Resource Blocks (RBs). In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency.
		\end{subsection}

		\begin{subsection}{IRS-aided SWIPT}
			The effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT. It was argued in \cite{Wu2019b} that dedicated energy beam is not required to maximize the Weighted Sum-Power (WSP) for a multiuser IRS-assisted SWIPT system, which is power-inefficient and may cause interference. On the other hand, \cite{Tang2019} suggested that if the interference from energy signals can be cancelled, multiple energy beams are generally required for the max-min harvested power problem. \cite{Wu2019c} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update transmit precoders and IRS phase shifts while the outer layer updates the penalty coefficients. It demonstrated that Line-of-Sight (LoS) links can boost the harvested power because the rank-deficient channels are highly correlated. In such cases, a single energy stream can satisfy the energy constraints of all energy receivers.

			However, most existing IRS-assisted SWIPT papers relied on an oversimplified linear harvester model with focus on single-carrier transmission for separated information and energy receivers. Rectifier nonlinearity and co-localized receiver, acknowledged as key to practical and efficient SWIPT system design, have not yet been addressed in the relevant research. In this paper, we depart from a tractable harvester model and study an IRS-aided downlink MISO SWIPT system, where the user employs the received signal for both information decoding and energy harvesting. The contributions are as follows.

			In this paper, we marry the benefits of joint waveform and active beamforming optimization for SWIPT (accounting for nonlinearity) with the passive beamforming capability of IRS. The contribution of the paper are listed as follows. First, we introduce an novel IRS-aided SWIPT architecture based on a joint waveform, active and passive beamforming design. This architecture can be seen to IRS-aided SWIPT what [40] is to SWIPT. Specifically, we consider a multi-carrier IRS-aided downlink MISO SWIPT system where the IRS assists the information and energy transmission to a single user. A multicarrier unmodulated power waveform (deterministic multisine) is superposed to a multicarrier modulated information waveform to boost the energy transfer efficiency. The power and information waveforms and active beamforming at the transmitter, the phase shifts at the IRS and the splitting ratio at the receiver are jointly optimized to maximize the R-E tradeoff while accounting for the rectenna nonlinearity. This is the first paper to proposed such a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT. Note that existing IRS-aided SWIPT papers [36,37,38,39] focus on single-carrier transmissions and ignore the rectenna nonlinearity (and therefore assume the oversimplified and inaccurate linear model), which prevents from exploiting the waveform gain in SWIPT system design. On the contrary, this paper focus on multicarrier IRS-SWIPT and investigates the fundamental impact of harvester nonlinearity on joint waveform, active and passive beamforming design. Second, we formulate an optimization for this joint waveform, active and passive beamforming design so as to characterize the R-E region achieved by the proposed architecture. The R-E region characterization problem is transformed into multiple energy maximization problems subject to different rate constraints. To reduce the design complexity, we propose an Alternating Optimization (AO) algorithm that updates the channel and transceiver [Not clear yet what you mean by this, maybe you can be more explicit and say that you optimize alternatively the IRS weights (passive beamforming) and the waveform and active beamforming weights] iteratively based on Semidefinite Relaxation (SDR) and Geometric Programming (GP) techniques. [Here I would add one sentence that says: "In contrast to [...], ... " to explain how th optimization of IRS-aided SWIPT changes compared to SWIPT]. Third, we conduct numerical evaluations that demonstrate the benefit of the proposed architecture, and that the proposed algorithm can find a stationary point for all tested channel realizations. We demonstrate that dedicated power waveform can boost the energy transmission efficiency such that TS and PS are preferred at low SNR and high SNR, respectively. Also, IRS is shown to bring a significant channel amplification and R-E enhancement especially when deployed next to the transmitter or the receiver. Finally, the proposed adaptive IRS-aided SWIPT architecture and design outperform the benchmark schemes for broadband transmission, and the optimal IRS can be approximated in closed form for single transmit antenna narrowband SWIPT [This last sentence is not clear to me].

			[For the third contribution, we need to highlight the that the observations for SWIPT carries on to IRS-aided SWIPT, namely blablabla, but also highlight the new observations.]

			\textit{First}, we extend the SWIPT waveform design in \cite{Clerckx2018b} to the IRS case and investigate the passive beamforming issue.

			% single antenna, DoF -> new words. ff irs fs channel not all flexibility; active antenna -> frequency

			We investigate the impact of IRS development on precoder design, waveform preference and transceiving strategy. Comparison is made with the no IRS case to highlight the benefit of introducing IRS in SWIPT systems.

			\textit{Second},

			Each achievable R-E pair is obtained through an Alternating Optimization (AO) algorithm that updates the IRS reflection coefficients

			and transceiver iteratively based on Semidefinite Relaxation (SDR) and Geometric Programming (GP) techniques.
		\end{subsection}

@@

			\textit{Organization:} The rest of this paper is organized as follows. Section~\ref{se:system_model} introduces the signal, channel, receiver and R-E tradeoff models of the IRS-aided SWIPT system. Section~\ref{se:problem_formulation} tackles the waveform, active and passive beamforming optimization. Section~\ref{se:performance_evaluation} presents simulation results to evaluate the proposed design. Section~[TODO] concludes the paper.

			\textit{Notations:} Scalars are denoted by italic letters, vectors are denoted by bold lower-case letters, and matrices are denoted by bold upper-case letters. $j$ refers to the imaginary unit. $\mathbb{C}^{x \times y}$ denotes the subspace spanned by complex $x \times y$ matrices. $\Re\{\cdot\}$ and $\Im\{\cdot\}$ stand for the real and imaginary part of a complex number or variable, respectively. $(\cdot)^*$, $(\cdot)^T$ and $(\cdot)^H$ represent the conjugate, transpose, and conjugate transpose operators, respectively. $\mathcal{A}\{\cdot\}$ extracts the DC component of a signal, and $\mathcal{E}_X\{\cdot\}$ takes the expectation over the distribution of the random variable $X$ ($X$ may be omitted for simplicity). For a scalar $x$, $\lvert{x}\rvert$ denotes its absolute value. For a vector $\boldsymbol{x}$, $\lVert{\boldsymbol{x}}\rVert$ refers to its Euclidean norm, $\arg(\boldsymbol{x})$ refers to its argument vector, and $\mathrm{diag}(\boldsymbol{x})$ refers to a square diagonal matrix with the elements of $\boldsymbol{x}$ on the main diagonal. For a general matrix $\boldsymbol{M}$, $\mathrm{rank}(\boldsymbol{M})$ denotes it rank. For a square matrix $S$, $\mathrm{Tr}(\boldsymbol{S})$ denotes its trace, and $\boldsymbol{S} \succeq 0$ means that $\boldsymbol{S}$ is positive semi-definite. The distribution of a random vector consists of Circularly Symmetric Complex Gaussian (CSCG) variables is denoted by $\mathcal{CN}(\boldsymbol{\mu},\boldsymbol{\Sigma})$, where $\boldsymbol{\mu}$ is the mean vector and $\boldsymbol{\Sigma}$ is the covariance matrix. $\sim$ means "distributed as". We also denote $(\cdot)^{\star}$ and $(\cdot)^{(i)}$ as stationary solution and solution at iteration $i$, respectively.
		\end{subsection}
	\end{section}

@@

		As shown in Fig.~\ref{fi:system}, we consider an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-reflector IRS, to a single-antenna user over $N$ orthogonal evenly-spaced subbands with center frequency $f_n$ ($n=1,\dots,N$). Perfect Channel State Information (CSI) at the transmitter, IRS and receiver with negligible training overhead are assumed to explore the upper bound of the proposed design. A quasi-static block fading channel model is considered for all links, and we focus on one particular block where the channels are approximately unchanged. Two practical co-located receiver architectures are compared in terms of R-E region. Specifically, TS divides each time slot into orthogonal data and energy slots and performs a time sharing between WPT and Wireless Information Transfer (WIT). In comparison, PS splits the received signal into individual ID and EH streams such that the splitting ratio $\rho$ is coupled with waveform and IRS design. Perfect synchronization is assumed among the three parties in both scenarios, and signals reflected by IRS for two and more times are omitted. We also assume the noise power is too small to be harvested.

@@

		\begin{subsection}{Composite Channel}
			At subband $n$, denote the AP-user direct channel as $\boldsymbol{h}_{D,n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$, and IRS-user reflective channel as $\boldsymbol{h}_{R,n}^H \in \mathbb{C}^{1 \times L}$. At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection amplitude $\gamma_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$~\footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\gamma_l=1\,,\forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}. Define the IRS matrix as $\boldsymbol{\Theta} = \mathrm{diag}(\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$ that collects the reflection coefficients onto its main diagonal entries. The extra link introduced by IRS can be modeled as a concatenation of the AP-IRS incident channel, IRS reflection matrix, and IRS-user reflective channel. On top of this, the total composite channel is obtained by superposing the IRS-aided extra channel to the AP-user direct channel as
			\begin{equation}\label{eq:h_n}
				\boldsymbol{h}_{n}^H = \boldsymbol{h}_{D,n}^H + \boldsymbol{h}_{R,n}^H \boldsymbol{\Theta} \boldsymbol{H}_{I,n} = \boldsymbol{h}_{D,n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n}
			\end{equation}
			where $\boldsymbol{\phi}=[\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{n}=\mathrm{diag}(\boldsymbol{h}_{R,n}^H)\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$. Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.
		\end{subsection}

@@

	\begin{section}{Problem Formulation}\label{se:problem_formulation}
		We characterize the R-E region through a current maximization problem subject to transmit power, IRS magnitude, and different rate constraints
		\begin{maxi!}
			{\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho}{z(\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho)}{\label{op:original}}{\label{ob:original}}
			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_I}\rVert^2+\lVert{\boldsymbol{w}_P}\rVert^2\right)\le{P}}\label{co:original_power}
			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_I,\rho) \ge \bar{R}}\label{co:original_rate}
			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}\label{co:original_modulus}
			\addConstraint{0 \le \rho \le 1\,.}
		\end{maxi!}
		Problem~\ref{op:original} is intricate due to the non-convex objective function \ref{ob:original} and the rate constraint \ref{co:original_rate} with coupled variables. To reduce the design complexity, we propose a suboptimal AO algorithm that iteratively updates the IRS phase shift and transmit waveform plus the receive splitting ratio until convergence.
